---
title: "IGF1R"
author: "Shelley"
date: "December 16, 2014"
output: html_document
---

This file contained the code for validating the IGF1R signature using ASSIGN

IGFR Summary
-------------------------------
IGFR1 is implicated in several cancers including breast, prostate, corectal, ovariam, scarcoma and lung cancers.

In breast cancer, EGFR inhibitors(erlotinib) are used to inhibit the EGFR signaling pathway, IGF-1R confers resistance by forming one half of a heterodimer , allowing EGFR signaling to resume in the presence of a suitable inhibitor. This process is referred to as crosstalk between EGFR and IGF-1R.

Causes resistance to Pi3K inhibitors

Increased levels of the IGF-IR are expressed in  primary/metastatic prostate cancer patient tumors, required for survival and growth when prostate cancer cells progress to androgen independence.

Gene amplification main mechanism for IGF1R overexpression

Target with an antibody or the tyrosine kinase: Linsitinib & dalotuzumab in clinical trials

```{r}
library(sva)
library(ASSIGN)
```

Read in the datasets
```{r}
setwd("~/Documents/ThesisWork/GitRepos/bild_signature_validation/Datasets")

GFP18_AKT_BAD_HER2_IGF1R_RAF_ERK <- as.matrix(read.table("~/Documents/ThesisWork/GitRepos/bild_signature_validation/Datasets/GFP18_AKT_BAD_HER2_IGF1R_RAF_ERK.tpmlog", stringsAsFactors=FALSE, row.names=1))

head(GFP18_AKT_BAD_HER2_IGF1R_RAF_ERK)
row.names(GFP18_AKT_BAD_HER2_IGF1R_RAF_ERK)
colnames(GFP18_AKT_BAD_HER2_IGF1R_RAF_ERK)

icbp<-as.matrix(read.table("ICBP/icbp_Rsubread_tpmlog.txt", sep='\t', stringsAsFactors=FALSE, header=1, row.names=1, check.names = FALSE))
head(icbp)
length(colnames(icbp))

gfp_IGF1R <-subset(GFP18_AKT_BAD_HER2_IGF1R_RAF_ERK,select=c(GFP.1:GFP.12,IGF1R.1:IGF1R.6))
head(gfp_IGF1R)
length(colnames(gfp_IGF1R))

# the 1 means by row name (gene names), if ~80% are zero then we don't want that gene 
gfp_IGF1R_1 <- gfp_IGF1R[apply(gfp_IGF1R[,1:17]==0,1,mean) < 0.8,]###if not removed over 83%; error occurs in batch adjustment
nrow(gfp_IGF1R_1)
removed= nrow(gfp_IGF1R)-nrow(gfp_IGF1R_1)
print( "number of genes removed after filtering = ") 
removed
```

Some function to make life easier :)
```{r}
merge_drop<-function(x,y,by=0)
{
  new_m<-merge(x,y,by=by)
  rownames(new_m)<-new_m$Row.names
  return(new_m[,2:length(colnames(new_m))])
}

pcaplot<-function(mat,sub,scale=T){
  if(sum(sub)!=length(mat)){
    print("verify the subscripts...exiting now")
    }
  else{
    pca_mat <- prcomp(t(mat), center=T,scale=scale)
    plot(pca_mat)
    plot(pca_mat$x[,1],pca_mat$x[,2])
    index= 1
    for(i in 1:length(sub)){
      #print(rownames(pca_mat$x)[index:sub[i]+index-1],"has color", )
      print(i)
      if(i==1){
        points(pca_mat$x[1:sub[i]],pca_mat$x[1:sub[i],2],col=i+1)
        }
      else if(i==length(sub)){
         points(pca_mat$x[index:length(rownames(pca_mat$x))],pca_mat$x[index:length(rownames(pca_mat$x)),2],col=i+1)
         }
      else{
        points(pca_mat$x[index:index+sub[i]],pca_mat$x[index:index+sub[i],2],col=i+1)
        }
       index=index+sub[i]
      }
  }
}
```


# Can use the commented out ones or not. Filtering out lowered expression or low varything genes 
# With adaptive and non-adaptive you don't really need too. It might make a different with non-adaptive 
```{r, cache=TRUE}
#AVG_IN <- apply(gfp_her2_1[,1:17], 1, mean)
#VAR_IN <- apply(gfp_her2_1[,1:17], 1, var)
#threshold_E <- sort(AVG_IN)[round(length(AVG_IN)*0.1)]
#threshold_V <- sort(VAR_IN)[round(length(VAR_IN)*0.1)]
#gfp_her2_1<- gfp_her2_1[which((AVG_IN > threshold_E)&(VAR_IN > threshold_V)),]
#nrow(gfp_her2_1)
# merging the test and traning data in order to use combat, need to be in the same matrix

dim(gfp_IGF1R_1)
gfp_IGF1R_1_icbp<-merge_drop(gfp_IGF1R_1,icbp,by=0)
dim(gfp_IGF1R_1_icbp)
head(gfp_IGF1R_1_icbp)
# specify the number of gfp,igf1r, and icbp
sub<-c(12,6,55)
#creates PCA to look at batch differences
pcaplot(mat =gfp_IGF1R_1_icbp,sub=sub)
```


Running combat with covariates
```{r}
bat1<-as.matrix(cbind(c(colnames(gfp_IGF1R_1),colnames(icbp)),c(rep(1,length(colnames(gfp_IGF1R_1))),rep(2,length(colnames(icbp)))),c(rep(1,12),rep(2,6),rep(1,55))))
bat1
bat1[,2]
bat1[,3]

mod <- model.matrix(~as.factor(bat1[,3]))
mod
combat_expr1<-ComBat(gfp_IGF1R_1_icbp, batch=bat1[,2], mod=mod, numCovs=NULL)
pcaplot(combat_expr1,sub)
```


Running combat without covariates
```{r}
##############Batch adjustment is needed############
# creating a matrix that tells combact which ones comes from which batch
bat2<-as.matrix(cbind(c(colnames(gfp_IGF1R_1),colnames(icbp)),c(rep(1,length(colnames(gfp_IGF1R_1))),rep(2,length(colnames(icbp))))))
bat2
bat2[,2]
# calls combat, and batch says what the batches for each sample are, usually always do "Null", using diff covariates did not get better results 
combat_expr2<-ComBat(dat=gfp_IGF1R_1_icbp, batch=bat2[,2], mod=NULL, numCovs=NULL)
# want to see them mixed together
pcaplot(combat_expr2,sub)
```

Run ASSIGN with no covariates and different number of genes
```{r}
ncol(combat_expr2)
trainingLabel1 <- list(control = list(igf1r=1:12), igf1r=13:18) 
trainingLabel1
# what are the labels for the training set
train_igfr1<-combat_expr2[,1:18] # 18 is training
head(train_igfr1)
test<-combat_expr2[,19:73] # the test
head(train_igfr1)
head(test)
ncol(test)
ncol(train_igfr1)

#create the output directory for ASSIGN 
dir.create("igf1r_single_100_adap_tpmlog_v2/")#, 
set.seed(1234)
assign.wrapper(trainingData=train_igfr1, testData=test, trainingLabel=trainingLabel1, testLabel=NULL, geneList=NULL, n_sigGene=100, adaptive_B=T, adaptive_S=F, mixture_beta=F, outputDir="igf1r_single_100_adap_tpmlog_v2/", theta0=0.05, theta1=0.9, iter=2000, burn_in=1000)

dir.create("igfr1_single_100_nonadap_tmplog_v2/")#, 
set.seed(1234)
assign.wrapper(trainingData=train_igfr1, testData=test, trainingLabel=trainingLabel1, testLabel=NULL, geneList=NULL, n_sigGene=100, adaptive_B=F, adaptive_S=F, mixture_beta=F, outputDir="igfr1_single_100_nonadap_tmplog_v2/", theta0=0.05, theta1=0.9, iter=2000, burn_in=1000)

# Now try with 50 genes
dir.create("igf1r_single_50_adap_tpmlog_v2/")#, 
set.seed(1234)
assign.wrapper(trainingData=train_igfr1, testData=test, trainingLabel=trainingLabel1, testLabel=NULL, geneList=NULL, n_sigGene=50, adaptive_B=T, adaptive_S=F, mixture_beta=F, outputDir="igf1r_single_50_adap_tpmlog_v2/", theta0=0.05, theta1=0.9, iter=2000, burn_in=1000)

dir.create("igfr1_single_50_nonadap_tmplog_v2/")#, 
set.seed(1234)
assign.wrapper(trainingData=train_igfr1, testData=test, trainingLabel=trainingLabel1, testLabel=NULL, geneList=NULL, n_sigGene=50, adaptive_B=F, adaptive_S=F, mixture_beta=F, outputDir="igfr1_single_50_nonadap_tmplog_v2/", theta0=0.05, theta1=0.9, iter=2000, burn_in=1000)

# Now try with 25 genes
dir.create("igf1r_single_25_adap_tpmlog_v2/")#, 
set.seed(1234)
assign.wrapper(trainingData=train_igfr1, testData=test, trainingLabel=trainingLabel1, testLabel=NULL, geneList=NULL, n_sigGene=25, adaptive_B=T, adaptive_S=F, mixture_beta=F, outputDir="igf1r_single_25_adap_tpmlog_v2/", theta0=0.05, theta1=0.9, iter=2000, burn_in=1000)

dir.create("igfr1_single_25_nonadap_tmplog_v2/")#, 
set.seed(1234)
assign.wrapper(trainingData=train_igfr1, testData=test, trainingLabel=trainingLabel1, testLabel=NULL, geneList=NULL, n_sigGene=25, adaptive_B=F, adaptive_S=F, mixture_beta=F, outputDir="igfr1_single_25_nonadap_tmplog_v2/", theta0=0.05, theta1=0.9, iter=2000, burn_in=1000)


# background adjustment will take into account other varitions not addressed by combat. 
# adaptive = it will it into account, could be too much, could be too little
# nonadaptive= means dont worry it, don't do anything. LIKE BINREG, good comparion
# mooms been doing both. 
```

Run ASSIGN with covariates for difffernt numbers of genes
```{r}
ncol(combat_expr1)
trainingLabel1 <- list(control = list(igf1r=1:12), igf1r=13:18) 
trainingLabel1
# what are the labels for the training set
train_igfr1_1<-combat_expr1[,1:18] # 18 is training
head(train_igfr1_1)
test_1<-combat_expr1[,19:73] # the test
head(test_1)

#create the output directory for ASSIGN 
dir.create("igf1r_single_100_adap_tpmlog_v2_coVar/")#, 
set.seed(1234)
assign.wrapper(trainingData=train_igfr1_1, testData=test_1, trainingLabel=trainingLabel1, testLabel=NULL, geneList=NULL, n_sigGene=100, adaptive_B=T, adaptive_S=F, mixture_beta=F, outputDir="igf1r_single_100_adap_tpmlog_v2_coVar/", theta0=0.05, theta1=0.9, iter=2000, burn_in=1000)

dir.create("igf1r_single_100_nonadap_tmplog_v2_coVar/")#, 
set.seed(1234)
assign.wrapper(trainingData=train_igfr1_1, testData=test_1, trainingLabel=trainingLabel1, testLabel=NULL, geneList=NULL, n_sigGene=100, adaptive_B=F, adaptive_S=F, mixture_beta=F, outputDir="igf1r_single_100_nonadap_tmplog_v2_coVar/", theta0=0.05, theta1=0.9, iter=2000, burn_in=1000)

# try 50
dir.create("igf1r_single_50_adap_tpmlog_v2_coVar/")#, 
set.seed(1234)
assign.wrapper(trainingData=train_igfr1_1, testData=test_1, trainingLabel=trainingLabel1, testLabel=NULL, geneList=NULL, n_sigGene=50, adaptive_B=T, adaptive_S=F, mixture_beta=F, outputDir="igf1r_single_50_adap_tpmlog_v2_coVar/", theta0=0.05, theta1=0.9, iter=2000, burn_in=1000)

dir.create("igf1r_single_50_nonadap_tmplog_v2_coVar/")#, 
set.seed(1234)
assign.wrapper(trainingData=train_igfr1_1, testData=test_1, trainingLabel=trainingLabel1, testLabel=NULL, geneList=NULL, n_sigGene=50, adaptive_B=F, adaptive_S=F, mixture_beta=F, outputDir="igf1r_single_50_nonadap_tmplog_v2_coVar/", theta0=0.05, theta1=0.9, iter=2000, burn_in=1000)

# and 25 genes

dir.create("igf1r_single_25_adap_tpmlog_v2_coVar/")#, 
set.seed(1234)
assign.wrapper(trainingData=train_igfr1_1, testData=test_1, trainingLabel=trainingLabel1, testLabel=NULL, geneList=NULL, n_sigGene=25, adaptive_B=T, adaptive_S=F, mixture_beta=F, outputDir="igf1r_single_25_adap_tpmlog_v2_coVar/", theta0=0.05, theta1=0.9, iter=2000, burn_in=1000)

dir.create("igf1r_single_25_nonadap_tmplog_v2_coVar/")#, 
set.seed(1234)
assign.wrapper(trainingData=train_igfr1_1, testData=test_1, trainingLabel=trainingLabel1, testLabel=NULL, geneList=NULL, n_sigGene=25, adaptive_B=F, adaptive_S=F, mixture_beta=F, outputDir="igf1r_single_25_nonadap_tmplog_v2_coVar/", theta0=0.05, theta1=0.9, iter=2000, burn_in=1000)
```


Making the File with all the ASSIGN Corelations
```{r}
getwd()
filenames<-system("ls /Users/shelley/Documents/ThesisWork/GitRepos/bild_signature_validation/Results/IGF1R/*/pathway_activity_testset*", intern=TRUE)
filenames

for(i in 1:length(filenames)){
   f<-read.csv(filenames[i], header=1,row.names=1) ###reading in the files one at a time
  colnames(f)<-filenames[i]
  if(i==1){
    data<-f
  }else{
    data<-cbind(data,f)
  }
}

data
head(data)
dim(data)
row.names(data)
```


Combine the ASSIGN results with the ICBP data and Correlate with ICBP drug response data
-log(G150) = drug sensitivity, expect to see a positive corelation with rereg pathway. 
```{r}
ICBP_drugs <- read.delim("~/Documents/ThesisWork/GitRepos/bild_signature_validation/Datasets/ICBP_drugs_1.txt", row.names=1)
row.names(ICBP_drugs)
dim(ICBP_drugs)

results_icbp<-merge(data, ICBP_drugs ,by=0)

# missing three cell lines from the orinal ICBP data set
dim(results_icbp)
results_icbp

summary(results_icbp$Tykerb.IGF1R..1.1.)

# Correlations between Predictions and Drug response data (only response data for 35 cells lines)
# does a correlation anaylsis really do use justice since the spread of the response data is not that large??

#IGF1R inhibitor
cor(results_icbp[,2],results_icbp$Tykerb.IGF1R..1.1., use="complete.obs") # igf1r_single_100_adap_tpmlog_v2 , 0.01277489
cor(results_icbp[,11],results_icbp$Tykerb.IGF1R..1.1., use="complete.obs") #igfr1_single_100_nonadap_tmplog_v2 , 0.01094297

cor(results_icbp[,3],results_icbp$Tykerb.IGF1R..1.1., use="complete.obs") #igf1r_single_100_adap_tpmlog_v2_coVar, -0.1638966
cor(results_icbp[,4],results_icbp$Tykerb.IGF1R..1.1., use="complete.obs") #igf1r_single_100_nonadap_tmplog_v2_coVar, -0.09611917

cor(results_icbp[,5],results_icbp$Tykerb.IGF1R..1.1., use="complete.obs") #igf1r_single_25_adap_tpmlog_v2, -0.1197104
cor(results_icbp[,12],results_icbp$Tykerb.IGF1R..1.1., use="complete.obs") # igfr1_single_25_nonadap_tmplog_v2, -0.1230504

cor(results_icbp[,6],results_icbp$Tykerb.IGF1R..1.1., use="complete.obs") #igf1r_single_25_adap_tpmlog_v2_coVar,-0.1616389
cor(results_icbp[,7],results_icbp$Tykerb.IGF1R..1.1., use="complete.obs") #igf1r_single_25_nonadap_tmplog_v2_coVar, -0.1257636

cor(results_icbp[,8],results_icbp$Tykerb.IGF1R..1.1., use="complete.obs") #igf1r_single_50_adap_tpmlog_v2, -0.1430332
cor(results_icbp[,13],results_icbp$Tykerb.IGF1R..1.1., use="complete.obs") # igfr1_single_50_nonadap_tmplog_v2 -0.1441474

cor(results_icbp[,9],results_icbp$Tykerb.IGF1R..1.1., use="complete.obs") # igf1r_single_50_adap_tpmlog_v2_coVar, -0.2041042
cor(results_icbp[,10],results_icbp$Tykerb.IGF1R..1.1., use="complete.obs") #igf1r_single_50_nonadap_tmplog_v2_coVar, -0.1424113

Over all: IGFR1 inhibitor (Tykerb.IGF1R..1.1.) is not a good validation. Does not work that well. Might be because it also targets other pathways.
```

Correlate Drug Response with a Different IGF1R inhibitor(GSK1838705)
```{r}

results_icbp$GSK1838705
cor(results_icbp[,2],results_icbp$GSK1838705, use="complete.obs") # igf1r_single_100_adap_tpmlog_v2 , -0.3453591
cor(results_icbp[,11],results_icbp$GSK1838705, use="complete.obs") #igfr1_single_100_nonadap_tmplog_v2 , -0.3469378

cor(results_icbp[,3],results_icbp$GSK1838705, use="complete.obs") #igf1r_single_100_adap_tpmlog_v2_coVar, -0.5006833
cor(results_icbp[,4],results_icbp$GSK1838705, use="complete.obs") #igf1r_single_100_nonadap_tmplog_v2_coVar,-0.4119899

cor(results_icbp[,5],results_icbp$GSK1838705, use="complete.obs") #igf1r_single_25_adap_tpmlog_v2, -0.2674597
cor(results_icbp[,12],results_icbp$GSK1838705, use="complete.obs") # igfr1_single_25_nonadap_tmplog_v2, -0.2720832

cor(results_icbp[,6],results_icbp$GSK1838705, use="complete.obs") #igf1r_single_25_adap_tpmlog_v2_coVar, -0.4662894
cor(results_icbp[,7],results_icbp$GSK1838705, use="complete.obs") #igf1r_single_25_nonadap_tmplog_v2_coVar, -0.4130507

cor(results_icbp[,8],results_icbp$GSK1838705, use="complete.obs") #igf1r_single_50_adap_tpmlog_v2, -0.4055626
cor(results_icbp[,13],results_icbp$GSK1838705, use="complete.obs") # igfr1_single_50_nonadap_tmplog_v2, -0.4131063

cor(results_icbp[,9],results_icbp$GSK1838705, use="complete.obs") # igf1r_single_50_adap_tpmlog_v2_coVar,-0.5023617
cor(results_icbp[,10],results_icbp$GSK1838705, use="complete.obs") #igf1r_single_50_nonadap_tmplog_v2_coVar, -0.3978805

Over all: Better but negative may be use to its ALK inhibition, may ALK is inverse in these cells.
  100 genes with covariates is the bestm 25 with no variaties is good, and 50 with co variaties is too. But its negative?
```


Correlate with AKT inhibitor: Looks good
```{r}
cor(results_icbp[,2],results_icbp$Sigma.AKT1.2.inhibitor, use="complete.obs") # igf1r_single_100_adap_tpmlog_v2 , 0.4864112
cor(results_icbp[,11],results_icbp$Sigma.AKT1.2.inhibitor, use="complete.obs") #igfr1_single_100_nonadap_tmplog_v2 , 0.4863322

cor(results_icbp[,3],results_icbp$Sigma.AKT1.2.inhibitor, use="complete.obs") #igf1r_single_100_adap_tpmlog_v2_coVar, 0.3182924
cor(results_icbp[,4],results_icbp$Sigma.AKT1.2.inhibitor, use="complete.obs") #igf1r_single_100_nonadap_tmplog_v2_coVar, 0.3049189

cor(results_icbp[,5],results_icbp$Sigma.AKT1.2.inhibitor, use="complete.obs") #igf1r_single_25_adap_tpmlog_v2, 0.5445731
cor(results_icbp[,12],results_icbp$Sigma.AKT1.2.inhibitor, use="complete.obs") # igfr1_single_25_nonadap_tmplog_v2,  0.5448916

cor(results_icbp[,6],results_icbp$Sigma.AKT1.2.inhibitor, use="complete.obs") #igf1r_single_25_adap_tpmlog_v2_coVar,0.3006561
cor(results_icbp[,7],results_icbp$Sigma.AKT1.2.inhibitor, use="complete.obs") #igf1r_single_25_nonadap_tmplog_v2_coVar, 0.2629175

cor(results_icbp[,8],results_icbp$Sigma.AKT1.2.inhibitor, use="complete.obs") #igf1r_single_50_adap_tpmlog_v2, 0.3784261
cor(results_icbp[,13],results_icbp$Sigma.AKT1.2.inhibitor, use="complete.obs") # igfr1_single_50_nonadap_tmplog_v2, 0.3765225

cor(results_icbp[,9],results_icbp$Sigma.AKT1.2.inhibitor, use="complete.obs") # igf1r_single_50_adap_tpmlog_v2_coVar, 0.311552
cor(results_icbp[,10],results_icbp$Sigma.AKT1.2.inhibitor, use="complete.obs") #igf1r_single_50_nonadap_tmplog_v2_coVar,0.2879709

Overall: Adaptive vs. Not-adaptive does not seem to make a big differnce without co-variates, but adaptive seems to be working better when using co-variates.
The use of co-variates is always worse.
25 genes is the best, so far. 

#AKT inhbitor did not work well: not a good drug
cor(results_icbp[,2],results_icbp$Triciribine, use="complete.obs") # 0.02115863
cor(results_icbp[,11],results_icbp$Triciribine, use="complete.obs") #  -0.1812215
cor(results_icbp[,3],results_icbp$Triciribine, use="complete.obs") #
cor(results_icbp[,4],results_icbp$Triciribine, use="complete.obs") #
cor(results_icbp[,5],results_icbp$Triciribine, use="complete.obs") #
cor(results_icbp[,12],results_icbp$Triciribine, use="complete.obs") #
cor(results_icbp[,6],results_icbp$Triciribine, use="complete.obs") #
cor(results_icbp[,7],results_icbp$Triciribine, use="complete.obs")#
cor(results_icbp[,8],results_icbp$Triciribine, use="complete.obs") # 0.00240436
cor(results_icbp[,13],results_icbp$Triciribine, use="complete.obs") #
cor(results_icbp[,9],results_icbp$Triciribine, use="complete.obs") #
cor(results_icbp[,10],results_icbp$Triciribine, use="complete.obs") # -0.2410229

Overall: really bad higest -0.24
```

Read in the IFGR binReg Results

The probabilties don't really change much with the more genes you add. 
The coefficnt goes down as you add more genes to the model. 
q and Dwd have similar model numbers
100-dwd bild-1 - alot with the contols, heat map looks good, not too many high ones
200-dwd bild-1 - good, probilties so up as you add more genes
300-dwd bild-1
400-dwd bild-1
500-dwd bild-1

Probailites a litter high with 200 and 300 genes than 100 or 500
Higher weight of IGFR1 with less genes
100-q-1 meta -  many with controls, similar to dwd bild
200-q-1 meta
300-q-1 meta 
400-q-1 meta
500-q-1 meta

NO to DWD Normaliztin, it over predicts
NO to all with 2 meta genes

Read in the BinReg Files
```{r}
#binRegFile100_dwdbild_1=read.delim("~/Documents/ThesisWork/GitRepos/bild_signature_validation/Results/IGF1R/BinReg/IGFIR/IGFIR_ICBP_1Metagene_100_--dwd_bild/probabilities.txt")
                                 
binRegFile200_dwdbild_1=read.delim("~/Documents/ThesisWork/GitRepos/bild_signature_validation/Results/IGF1R/BinReg/IGFIR/IGFIR_ICBP_1Metagene_200_--dwd_bild/probabilities.txt")

summary(binRegFile200_dwdbild_1)
binRegFile200_dwdbild_1$Sample
dim(binRegFile200_dwdbild_1) #91 x 9
head(binRegFile200_dwdbild_1)

#ICBPcells_100=binRegFile100_dwdbild_1[37:nrow(binRegFile100_dwdbild_1),]
ICBPcells_200=binRegFile200_dwdbild_1[37:nrow(binRegFile200_dwdbild_1),]

#ICBPsamples_100 = ICBPcells_100$Sample
ICBPsamples_200 = ICBPcells_200$Sample
ICBPsamples_200
dim(ICBPcells_200) # 55 x 9
ICBPprobs= subset(ICBPcells_200, select=c("Probability"))
ICBPprobs
ICBPprobTable= data.frame(ICBPsamples_200,ICBPprobs)
class(ICBPprobTable)
row.names(ICBPprobTable)=ICBPsamples_200
ICBPprobTable$ICBPsamples <- NULL
head(ICBPprobTable)

dim(ICBP_drugs)
dim(ICBPprobTable)
ICBP_Probs_Drugs=merge(ICBPprobTable,ICBP_drugs, by=0)
View(ICBP_Probs_Drugs)
#ICBP_Probs_Drugs=merge(ICBPprobTable,ICBP_drugs, by=0, all.x=TRUE) #keeps all
#dim(ICBP_Probs_Drugs)

cor(ICBP_Probs_Drugs$Probability, ICBP_Probs_Drugs$Tykerb.IGF1R..1.1., use="complete.obs") #-0.06019889
cor(ICBP_Probs_Drugs$Probability, ICBP_Probs_Drugs$Sigma.AKT1.2.inhibitor, use="complete.obs") #0.4225113
cor(ICBP_Probs_Drugs$Probability, ICBP_Probs_Drugs$Triciribine, use="complete.obs") #-0.2322041 
cor(ICBP_Probs_Drugs$Probability, ICBP_Probs_Drugs$GSK1838705, use="complete.obs") #-0.274716  Also negative with ASSIGN
cor(ICBP_Probs_Drugs$Probability, ICBP_Probs_Drugs$AS.252424, use="complete.obs") # 0.2053028 Pi3k

cor(ICBP_Probs_Drugs$Probability, ICBP_Probs_Drugs$BEZ235, use="complete.obs") # 0.1519295, Pi3k/mTOR
cor(ICBP_Probs_Drugs$Probability, ICBP_Probs_Drugs$GSK2119563, use="complete.obs") # 0.2428557 PI3K
cor(ICBP_Probs_Drugs$Probability, ICBP_Probs_Drugs$GSK2126458, use="complete.obs") # 0.2652762 PI3K
cor(ICBP_Probs_Drugs$Probability, ICBP_Probs_Drugs$GSK1059615, use="complete.obs") # -0.1192411 PI3K
cor(ICBP_Probs_Drugs$Probability, ICBP_Probs_Drugs$PF.4691502, use="complete.obs") # -0.2622142 PI3K
cor(ICBP_Probs_Drugs$Probability, ICBP_Probs_Drugs$Temsirolimus, use="complete.obs") # --0.1111335 mTor

#Negative Controls
cor(ICBP_Probs_Drugs$Probability, ICBP_Probs_Drugs$Tamoxifen, use="complete.obs") # -0.15893 NEG
cor(ICBP_Probs_Drugs$Probability, ICBP_Probs_Drugs$Velcade, use="complete.obs") # -0.05099915 PROTESOME
```


Reading in ccle CNV data to Correlate with ASSIGN predictions and filtering for Breast cell lines only
```{r}
ccle_cnv<-read.table("CCLE/CCLE_copynumber_byGene_2013-12-03.txt", header=1)
rownames(ccle_cnv)<-ccle_cnv$SYMBOL
igf1r_cnv<-ccle_cnv["IGF1R",]

igf1r_interested_cnv<-igf1r_cnv[,grep("_BREAST",colnames(igf1r_cnv))]
colnames(igf1r_interested_cnv)
colnames(igf1r_interested_cnv)<-gsub(pattern = "_BREAST",replacement = "",colnames(igf1r_interested_cnv)) 
colnames(igf1r_interested_cnv)
```


Now, moving on to correlating the IGF1R predictions with CNV data from CCLE 
```{r}
results_ccle<-merge_drop(data,t(igf1r_interested_cnv["IGF1R",]),by=0)
View(results_ccle)
colnames(results_ccle)

#corrlate the ASSIGN predictions without covaritates with IGF1R CNV data
cor(results_ccle[,1], final_mat$IGF1R) #100_adap   -0.04465064
cor(results_ccle[,2], final_mat$IGF1R) # 100_adap_tpmlog_v2_coVar, 0.3093737
cor(results_ccle[,3], final_mat$IGF1R) # 100_nonadap_tmplog_v2_coVar, 0.2304624
cor(results_ccle[,4], final_mat$IGF1R) # 25_adap_tpmlog_v2, -0.05442617
cor(results_ccle[,5], final_mat$IGF1R) # 25_adap_tpmlog_v2_coVar, 0.1438074
cor(results_ccle[,6], final_mat$IGF1R) # 25_nonadap_tmplog_v2_coVar, 0.09062539
cor(results_ccle[,7], final_mat$IGF1R) # 50_adap_tpmlog_v2,  -0.09469717
cor(results_ccle[,8], final_mat$IGF1R) # 50_adap_tpmlog_v2_coVar, 0.2364518
cor(results_ccle[,9], final_mat$IGF1R) # 50_nonadap_tmplog_v2_coVar, 0.1797137
cor(results_ccle[,10], final_mat$IGF1R) # 100_nonadap_tmplog_v2,  -0.04466689
cor(results_ccle[,11], final_mat$IGF1R) # single_25_nonadap_tmplog_v2, -0.05531753
cor(results_ccle[,12], final_mat$IGF1R) # 50_nonadap_tmplog_v2, -0.09929077

Over all : Highest correlation is 0.30
  Using the co-variates gave the highest corelation, 100 genes nonadaptive was better, and 50 adap and 100 non adat where similar. 

```


Print the time
```{r echo=FALSE}
time<-format(Sys.time(),"%a %b %d %X %Y")
time
```
This analysis was run on `r time` 