---
title: "ERK Signature Validation with ICBP drug response data"
author: "Shelley"
date: "December 17, 2014"
output: pdf_document
---

```{r include=FALSE}
library(sva)
library(ASSIGN)
setwd("~/Documents/ThesisWork/GitRepos/bild_signatures/Rmarkdowns_scripts")
source("Key_ASSIGN_functions.Rmd")
```

Reading datasets and batch adjusting
```{r, cache=TRUE, include=FALSE}
feature<-as.matrix(read.table("~/Documents/ThesisWork/GitRepos/bild_signature_validation_old_repo/Datasets/GFP18_AKT_BAD_HER2_IGF1R_RAF_ERK.tpmlog", sep='\t', stringsAsFactors=FALSE, header=1, row.names=1))
head(feature)
icbp<-as.matrix(read.table("~/Documents/ThesisWork/GitRepos/bild_signature_validation_old_repo/Datasets/ICBP/icbp_Rsubread_tpmlog.txt", sep='\t', stringsAsFactors=FALSE, header=1, row.names=1))
head(icbp)

gfp_erk<-subset(feature,select=c(GFP.1:GFP.12,ERK.1:ERK.6))
head(gfp_erk)
dim(gfp_erk)
gfp_erk_1 <- gfp_erk[apply(gfp_erk[,1:18]==0,1,mean) < 0.8,]###if not removed over 83%; error occurs in batch adjustment
dim(gfp_erk) #didnt remove any

gfp_erk_1_icbp<-merge_drop(gfp_erk_1,icbp,by=0)
head(gfp_erk_1_icbp)

sub<-c(12,6,55)

pcaplot(mat = gfp_erk_1_icbp,sub=sub)
##############Batch adjustment is needed############
#with covariates

bat1_erk<-as.matrix(cbind(c(colnames(gfp_erk_1),colnames(icbp)),c(rep(1,length(colnames(gfp_erk_1))),rep(2,length(colnames(icbp)))),c(rep(1,12),rep(2,6),rep(1,length(colnames(icbp))))))
bat1_erk
bat1[,2]

#mod <- model.matrix(~as.factor(bat1[,3]))
#combat_expr1_erk<-ComBat(dat=gfp_erk_1_icbp, batch=bat1_erk[,2], mod=mod, numCovs=NULL)
#pcaplot(mat = combat_expr1,sub=sub)

#Combat without covariates
combat_expr2_erk<-ComBat(dat=gfp_erk_1_icbp, batch=bat1_erk[,2], mod=NULL, numCovs=NULL)
pcaplot(mat = combat_expr2_erk,sub=sub) #looks good

```

##########calling ASSIGN########
```{r}
train_erk<-combat_expr2_erk[,1:18] ; head(train_erk)
test_erk<-combat_expr2_erk[,19:73]
head(test_erk)
trainingLabel1=list(control = list(erk=1:12), erk = 13:18)
dir.create("~/Documents/ThesisWork/GitRepos/bild_signatures/Results/Validating_Signatures/ERK")
outdir150="~/Documents/ThesisWork/GitRepos/bild_signatures/Results/Validating_Signatures/ERK"
assign_easy_multi(trainingData=train_erk, testData = test_erk,trainingLabel1=trainingLabel1,g=150,out_dir_base=outdir150)

dir.create("~/Documents/ThesisWork/GitRepos/bild_signatures/Results/Validating_Signatures/ERK250")
outdir250="~/Documents/ThesisWork/GitRepos/bild_signatures/Results/Validating_Signatures/ERK250"
assign_easy_multi(trainingData=train_erk, testData = test_erk,trainingLabel1=trainingLabel1,g=250,out_dir_base=outdir250)

outdir200="~/Documents/ThesisWork/GitRepos/bild_signatures/Results/Validating_Signatures/ERK200"
dir.create(outdir200)
assign_easy_multi(trainingData=train_erk, testData = test_erk,trainingLabel1=trainingLabel1,g=200,out_dir_base=outdir200)

outdir100="~/Documents/ThesisWork/GitRepos/bild_signatures/Results/Validating_Signatures/ERK100"
dir.create(outdir100)
assign_easy_multi(trainingData=train_erk, testData = test_erk,trainingLabel1=trainingLabel1,g=100,out_dir_base=outdir100)

outdir50="~/Documents/ThesisWork/GitRepos/bild_signatures/Results/Validating_Signatures/ERK50"
dir.create(outdir50)
assign_easy_multi(trainingData=train_erk, testData = test_erk,trainingLabel1=trainingLabel1,g=50,out_dir_base=outdir50)

outdir75="~/Documents/ThesisWork/GitRepos/bild_signatures/Results/Validating_Signatures/ERK75"
dir.create(outdir75)
assign_easy_multi(trainingData=train_erk, testData = test_erk,trainingLabel1=trainingLabel1,g=75,out_dir_base=outdir75)

outdir25="~/Documents/ThesisWork/GitRepos/bild_signatures/Results/Validating_Signatures/ERK25"
dir.create(outdir25)
assign_easy_multi(trainingData=train_erk, testData = test_erk,trainingLabel1=trainingLabel1,g=25,out_dir_base=outdir25)
```

Attemping to get the gene lists into sperate files. GET Moom's help here!
```{r}

setwd("~/Documents/ThesisWork/GitRepos/bild_signatures/Results/Validating_Signatures/ERK/")
Routput_erk_files<-system("ls */*/output.rda* ", intern=TRUE)
Routput_erk_files

Routput_erk_files[1]

ERK = tmp=NULL
for(i in 1:length(Routput_erk_files)) {
  #filename=Routput_erk_files[i]
  i=3
  temp=getGeneList(Routput_erk_files[i])
  colnames(temp)=Routput_erk_files[i]
  temp1=temp
  print(temp)
  write.table(temp, "text_loop.txt" ,sep='\t', col.names = NA,quote=F, append= TRUE)
  #GeneLists=rbind(GeneLists,temp)  
  temp=NULL
  }
  
GeneLists

load("ERK100/adap_adap_multi/output.rda")
adap_adap=output.data$processed.data$S_matrix

load("ERK100/adap_multi/output.rda")
adap= output.data$processed.data$S_matrix

cor(adap_adap,adap) #same


# I think the gene lists are the same, but I can't tell if it is loading the same R data over and over again. 
ERK200_adap_adap= getGeneList("~/Documents/ThesisWork/GitRepos/bild_signatures/Results/Validating_Signatures/ERK/ERK200/adap_adap_multi/output.rda")
View(ERK200_adap_adap)
ERK200_adap= getGeneList("~/Documents/ThesisWork/GitRepos/bild_signatures/Results/Validating_Signatures/ERK/ERK200/adap_multi/output.rda")
View(ERK200_adap)
ERK200_nonadap= getGeneList("~/Documents/ThesisWork/GitRepos/bild_signatures/Results/Validating_Signatures/ERK/ERK200/nonadap_multi/output.rda")
View(ERK200_nonadap)

cor(ERK200_adap, ERK200_adap_adap)
cor(ERK200_nonadap, ERK200_adap_adap)

ERK75_adap_adap= getGeneList("~/Documents/ThesisWork/GitRepos/bild_signatures/Results/Validating_Signatures/ERK/ERK75/adap_adap_multi/output.rda")
View(ERK75_adap_adap)
ERK75_adap= getGeneList("~/Documents/ThesisWork/GitRepos/bild_signatures/Results/Validating_Signatures/ERK/ERK75/adap_multi/output.rda")
View(ERK75_adap)
ERK57_nonadap= getGeneList("~/Documents/ThesisWork/GitRepos/bild_signatures/Results/Validating_Signatures/ERK/ERK75/nonadap_multi/output.rda")
View(ERK57_nonadap)

```


Read in the predictions and correlate with eachother.
```{r}
setwd("~/Documents/ThesisWork/GitRepos/bild_signatures/Results/Validating_Signatures/ERK/")
filenames_erk<-system("ls */*/pathway_activity_testset* ", intern=TRUE)
length(filenames_erk)
filenames_erk

for(i in 1:length(filenames_erk))
  {
   f<-read.csv(filenames_erk[i], header=1,row.names=1) ###reading in the filess one at a time
  colnames(f)<-filenames_erk[i]
  if(i==1){
    data_erk<-f
    }
  else{
    data_erk<-cbind(data_erk,f)
    }
  }

data_erk ; dim(data_erk)
View(data_erk)
rownames(data_erk)
plot(1:55,data_erk[,1])

data_erk[1]

rownames(data_erk)[1:7]=(c("184A1",  "184B5", "21MT1","21MT2","21NT","21PT","600MPE"))
rownames(data_erk)[50]=(c("T47D_KBluc"))
rownames(data_erk)

# This just correlelates the predictions with eachother
correlate_predictions=cor(data_erk, method="spearman")
View(correlate_predictions)
#writeFile(correlate_predictions, "ERK_ICBP_PathwayPrediction_Correlations.txt")
#View(correlate_predictions)
plot(correlate)
View(correlate)

```
```

Not Really Working Right
```{r}
library( package = ISwR )


image(
    z    = cor( x = data_erk, method = "spearman" ),
    axes = FALSE,
    zlim = c( -1.0, 1.0 ) )


axis(
    side     = 1,
    labels   = names( data_erk ),
    at       = seq( 0, 1, length = length( names( data_erk ) ) ),
    cex.axis = 0.8,
    las = 2)

axis(
    side     = 2,
    labels   = names( data_erk ),
    at       = seq( 0, 1, length = length( names(data_erk ) ) ),
    cex.axis = 0.8,
    las =1 )

box()


```


Load in ICBP data, merge with pathway predictions
```{r, cache=TRUE}
ICBP_drugs<-read.delim("~/Documents/ThesisWork/GitRepos/bild_signature_validation_old_repo/Datasets/ICBP_drugs_1.txt", header=1, sep='\t',row.names=1)
# load in CCLE drug data for RAF


drugs=ICBP_drugs[,11:100] 
View(drugs)

# Merge drug respose and predictions
pred_drug_erk<-merge_drop(data_erk,drugs,by=0) ; dim(pred_drug_erk) # 53 x 111

pred_drug_erk_complete_only = pred_drug_erk[complete.cases(pred_drug_erk),]
=)

predicictionCols= (pred_drug_erk[,1:21]) ; dim(predicictionCols)
drugs_55_cell_lines=(pred_drug_erk[,22:111]) ; dim(drugs_55_cell_lines)
plot(drugs_55_cell_lines) 

View(drugs_55_cell_lines)
summary(drugs_55_cell_lines)
```


Correlation Parameters
------------------------
*Pairwise Correlations: parwise is computed using all complete pairs of observations on those variables. This can result in correlation matrices which are not positive semi-definite, as well as NA entries if there are no complete pairs for that pair of variables.

*Na.or.complete: Missing values are handled by casewise deletion (and if there are no complete cases, that gives an error).

Now we will correlate all the pathway predictions with all the drugs...
Here we see that we get better predictions and I think is is because we are removing the cell lines with NAs...?
```{r} 

cors_erk_preds_alldrugs_complete= cor(predicictionCols,drugs_55_cell_lines, use="pairwise",method= "spearman")
View(cors_erk_preds_alldrugs_complete)

#corr.test


#use this  if you want to get the p-values from the bootstrap
library(psych)

#rhos=p_val=NULL
#temp=temp_f=NULL
#for(i in 1:160){
#  for(j in 1:7) {
    #i=1
    #j=1
 # pathway_drug=subset(pred_drug_only, select=c(i,160+j))
#  temp_cors= cor.ci(pathway_drug, method="spearman", plot=FALSE)
#  temp<-c(temp_cors$rho[2,1],temp_cors$ci[5])  
#  temp<- cbind(temp[1],temp[2])
#  temp_f<-rbind(temp_f,temp)
#  rownames(temp_f)[j+(i-1)*7]=paste(colnames(pathway_drug)[1],colnames(pathway_drug)[2],sep='__')
#  }
#}
colnames(temp_f)<-c("Corr","p_val")


writeFile(cors_erk_preds_alldrugs_complete, "~/Documents/ThesisWork/GitRepos/bild_signatures/Results/Validating_Signatures/ERK/ERK_pathwaypredictions_ICBPdrugresponse_correlations_complete.txt")


```

We can use this package if we want to get the p-values from the correlations gives the same results at just using cor
```{r}
#this library will provide p-values for correlations 
library(psych)
erk_preds_alldrugs_pych_pairwise= corr.test(predicictionCols,drugs_55_cell_lines, use="pairwise",method= "spearman", adjust="none" )

dim(drugs_55_cell_lines)

View(erk_preds_alldrugs_pych_pairwise[1])

class(erk_preds_alldrugs_pych_pairwise)

View(erk_preds_alldrugs_pych_pairwise$r)

writeFile(erk_preds_alldrugs_pych_pairwise$r, "ICBP_erk_preds_alldrugs_pych_pairwise.txt")

erk_preds_alldrugs_pych_complete[3]



```


Plotting the ERK pathway predictions/drug respose correlations

Results: Adap_adap is almost always better, but are we overfitting???
- Adapative Background and NonAdaptive Background (both nonadap signature) look similar 
```{r}

names=gsub("*_multi/pathway_activity_testset.csv", "", rownames(cors_erk_preds_alldrugs_complete))
names
par(mar=c(11.1, 6.1, 4.1, 6.1))
plot(cors_erk_preds_alldrugs_complete$ERKi.II..FR180304., ylab= "Spearmean Correlation", main= "Correlation: ERK Inhibitor Response & Pathway Predictions", xlab=NA, xaxt="n" , col=1:3, cex.main=0.8)
points(1:5, col="red")
axis(1, at=1:21, labels=names, las=2)

# Looks like with 200 and 50 genes gives the higest predictions
# Adap_adp gives higest, and just adaptive alone or adapative/non adaptive are similar
# Could adap_adap be over fitting????

#now find a way to correlate with alll the drugs

#fist do a test
```


These are some tests with using different correlations settings
```{r}

#  1) Correlating with ERK inhibitor only not all the drugs
#       - Spearman Complete and Pairwise are the SAME(no additonal cell lines are being removed because we are long looking at 1 drug)
#       - Pearson looks better, but still is low
#       - 
#

# LOW predictions for NA or Complete with Spearman
erk_preds_erki_cors_naorcomp= cor(predicictionCols[,1], drugs_55_cell_lines$ERKi.II..FR180304.,use="na.or.complete",method= "spearman" )
View(erk_preds_erki_cors_naorcomp)
dim(erk_preds_erki_cors_naorcomp)


# Same as above
erk_preds_erki_cors_pair= cor(predicictionCols, drugs_55_cell_lines$ERKi.II..FR180304.,use="pairwise.complete.obs",method= "spearman" )
erk_preds_erki_cors_pair

# Pearson gives better prediction but are still really low
erk_preds_erki_cors_naorcomp= cor(predicictionCols, drugs_55_cell_lines$ERKi.II..FR180304.,use="na.or.complete",method= "pearson" )
erk_preds_erki_cors_naorcomp
# Same as above
erk_preds_erki_cors_pair_pearson= cor(predicictionCols, drugs_55_cell_lines$ERKi.II..FR180304.,use="pairwise.complete.obs",method= "pearson" )
erk_preds_erki_cors_pair_pearson

#Try with AGG drug just to make sure
erk_preds_AAG_cors_pair= cor(predicictionCols, drugs_55_cell_lines[1],use="pairwise.complete.obs",method= "spearman" )
erk_preds_AAG_cors_pair
# same
erk_preds_AAG_cors_pair= cor(predicictionCols, drugs_55_cell_lines[1],use="na.or.complete",method= "spearman" )
erk_preds_AAG_cors_pair
```


Looks like resistant cell lines have higer pathway predictions than sensitive.
But we would expect cell line with high pathway activity to be more sensitive
```{r}
# We expect to see cells lines that are sensitivt 
#subet the erk inhibitor response to retain row names
cellines = rownames(pred_drug_erk)
erk_sensitivity= pred_drug_erk$ERKi.II..FR180304
erk_sensitivty = cbind(cellines,erk_sensitivity)
class(erk_sensitivty)
erk_sensitivty[,1]

mode(pred_drug_erk$ERKi.II..FR180304)


# plot the drug sensitivity
plot(pred_drug_erk$ERKi.II..FR180304, main="Drug Sensitivity to ERKiII across ICBP Cell Lines", xlab= "Cell Line", ylab= "Sensitivity")
plot(pred_drug_erk$Erlotinib, main="Drug Sensitivity to Eroltinib across ICBP Cell Lines", xlab= "Cell Line", ylab= "Sensitivity")
plot(pred_drug_erk$BIBW2992, main="Drug Sensitivity to BIBW2992 across ICBP Cell Lines", xlab= "Cell Line", ylab= "Sensitivity")

#find the mean of response to all drugs
means_GI50 = colMeans(pred_drug_erk[,32:111], na.rm=TRUE)
means_GI50

median(ERKdrugpredictions, na.rm = TRUE)

#find the mean of response to ERKi 
erk_mean = means_GI50["ERKi.II..FR180304."] 
erk_mean

#seperate the cell lines into sensitive and resistant to erk inhibitor 
# Will will find a way to do this better with mclust later
erk_sensitive= subset(erk_sensitivty, erk_sensitivty[,2] > 4.5, )
erk_sensitive
rownames(erk_sensitive)
erk_resistent= subset(erk_sensitivty, erk_sensitivty[,2] < 4.5)
erk_resistent

####################################################################
#just do one first to keep it simple 
ERK100_adap_adap_sensitive = merge(data_erk[1],erk_sensitive,by.x=0, by.y=1)
ERK100_adap_adap_sensitive
ERK100_adap_adap_resistant = merge(data_erk[1], erk_resistent, by.x=0, by.y=1)
ERK100_adap_adap_resistant

cor(ERK100_adap_adap_sensitive[,2],as.numeric(ERK100_adap_adap_sensitive[,3]), use="na.or.complete",method= "spearman") # -0.41
cor(ERK100_adap_adap_resistant[,2],as.numeric(ERK100_adap_adap_resistant[,3]), use="na.or.complete",method= "spearman") # 0.28 

ERK100_adap_adap = t.test(ERK100_adap_adap_resistant[,2],ERK100_adap_adap_sensitive[,2])
pval = ERK100_adap_adap[3]

boxplot(ERK100_adap_adap_resistant[,2],ERK100_adap_adap_sensitive[,2], names=c("Resistant","Sensitive"), ylab= "pathway activity", main= gsub("_multi/pathway_activity_testset.csv", "", colnames(data_erk[1])))

#####################################################################

# now do it for all the predictions 
boxplot_erk =function(colnumber ) {
sensitive = merge(data_erk[colnumber],erk_sensitive,by.x=0, by.y=1) 
resistant = merge(data_erk[colnumber], erk_resistent, by.x=0, by.y=1)  

sensitive_cor = cor(sensitive[,2], as.numeric(sensitive[,3]), use="na.or.complete",method= "spearman") 
print("Correlation between sensitive cells line predictions and drug sensitivity") ; print(sensitive_cor)
resistant_cor = cor(resistant[,2],  as.numeric(resistant[,3]), use="na.or.complete",method= "spearman") 
print("Correlation between 'resistant' cells line predictions and drug sensitivity") ;print(resistant_cor)

ttest= t.test(resistant[,2],sensitive[,2]) ; pval = ttest[3] ; print("pval for resistant vs. sensitive pathway predictions") ; print(pval)

boxplot(resistant[,2],sensitive[,2], names=c("Resistant","Sensitive"), ylab= "pathway activity", main= gsub("_multi/pathway_activity_testset.csv", "", colnames(data_erk[colnumber])))
text(1,1, pval)
}


pdf("~/Desktop/boxplot_erk_validation.pdf")
# now plot them all
for (i in 1:ncol(data_erk)){
  
  boxplot_erk(i)
}
dev.off()

```


```{r echo=FALSE}
time<-format(Sys.time(),"%a %b %d %X %Y")
```
This analysis was run on `r time` 
