---
title: "ICBP_EGFRValidation"
author: "Shelley"
date: "November 14, 2014"
output: html_document
---
**Goal**
Validate EGFR signature with 

Read and clean the ICBP binReg Results
```{r}

binRegFile200=read.delim("~/Documents/ThesisWork/GitRepos/u01project/binregResults/EGFR/ICBP/EGFR_ICBP_1Metagene_dwd_200/probabilities.txt")
binRegFile250=read.delim("~/Documents/ThesisWork/GitRepos/u01project/binregResults/EGFR/ICBP/EGFR_ICBP_1Metagene_dwd_250/probabilities.txt")
head(binRegFile250)
binRegFile300=read.delim("~/Documents/ThesisWork/GitRepos/u01project/binregResults/EGFR/ICBP/EGFR_ICBP_1Metagene_dwd_300/probabilities.txt")
head(binRegFile300)
binRegFile350=read.delim("~/Documents/ThesisWork/GitRepos/u01project/binregResults/EGFR/ICBP/EGFR_ICBP_1Metagene_dwd_350/probabilities.txt")
binRegFile400=read.delim("~/Documents/ThesisWork/GitRepos/u01project/binregResults/EGFR/ICBP/EGFR_ICBP_1Metagene_dwd_400/probabilities.txt")
binRegFile450=read.delim("~/Documents/ThesisWork/GitRepos/u01project/binregResults/EGFR/ICBP/EGFR_ICBP_1Metagene_dwd_450/probabilities.txt")
binRegFile500=read.delim("~/Documents/ThesisWork/GitRepos/u01project/binregResults/EGFR/ICBP/EGFR_ICBP_1Metagene_dwd_500/probabilities.txt")

binRegFile= NULL
#binRegFile
binRegFile= binRegFile200
#binRegFile= binRegFile250
#binRegFile= binRegFile300
#binRegFile= binRegFile350
#binRegFile= binRegFile400
#binRegFile= binRegFile450
 
#binRegFile= binRegFile500



summary(binRegFile)
binRegFile$Sample
dim(binRegFile) #91

ICBPcells=binRegFile[37:nrow(binRegFile),]
ICBPsamples = ICBPcells$Sample
ICBPsamples
dim(ICBPcells) # 55
ICBPprobs= subset(ICBPcells, select=c("Probability"))
ICBPprobs
ICBPprobTable= data.frame(ICBPsamples,ICBPprobs)
class(ICBPprobTable)
row.names(ICBPprobTable)=ICBPsamples
ICBPprobTable$ICBPsamples <- NULL
head(ICBPprobTable)

```


Read in the drug data
```{r}
drugFile=read.delim("~/Documents/ThesisWork/GitRepos/u01project/SignatureValidations/EGFR/ICBP/ICBP_drugs.txt", row.names=1)
head(drugFile)
summary(drugFile)
EGFRdrugs=subset(drugFile, select= c("Transcriptional.subtype...ERBB2.status", "Lapatinib", "AG1478", "Gefitinib", "BIBW2992", "Erlotinib")) 
summary(EGFRdrugs)
```

```{r}
ICBP_Probs_Drugs=merge(ICBPprobTable,EGFRdrugs, by=0)
ICBP_Probs_Drugs
ICBP_Probs_Drugs=merge(ICBPprobTable,EGFRdrugs, by=0, all.x=TRUE)
ICBP_Probs_Drugs
```

Look at the distrubtion of the drugs IC50s
```{r}
hist(ICBP_Probs_Drugs$Lapatinib)
hist(ICBP_Probs_Drugs$AG1478)
hist(ICBP_Probs_Drugs$Gefitinib)
hist(ICBP_Probs_Drugs$BIBW2992)
hist(ICBP_Probs_Drugs$Erlotinib)
```

We would expect to see that there is a positive correlation between EGFR inhibitors and the probabilities
```{r}
summary(ICBP_Probs_Drugs)
hist(ICBP_Probs_Drugs$Probability)

#for 200
c1=cor(ICBP_Probs_Drugs$Probability, ICBP_Probs_Drugs$Lapatinib, use = "na.or.complete") #-0.2658951
print(c1)
c2=cor(ICBP_Probs_Drugs$Probability, ICBP_Probs_Drugs$AG1478, use = "na.or.complete") #-0.04543915
print(c2)
c3=cor(ICBP_Probs_Drugs$Probability, ICBP_Probs_Drugs$Gefitinib, use = "na.or.complete") #-0.1673386
print(c3)
c4=cor(ICBP_Probs_Drugs$Probability, ICBP_Probs_Drugs$BIBW2992, use = "na.or.complete") #-0.2893571
print(c4)
c5=cor(ICBP_Probs_Drugs$Probability, ICBP_Probs_Drugs$Erlotinib, use = "na.or.complete")#-0.1118872
print(c5)

#for 250
[1] -0.2249219  
[1] -0.1079417
[1] -0.2127953
[1] -0.2754292
[1] -0.1905705

#for 300
[1] -0.2024346
[1] -0.05193612
print(c3)
[1] -0.176239
print(c4)

> print(c5)
[1] -0.1490065
#for 350

[1] -0.204828
[1] -0.02165414
[1] -0.1563606
[1] -0.2255205
[1] -0.142113

#for 400
> print(c1)
[1] -0.1880711
> print(c2)
[1] -0.03276945
> print(c3)
[1] -0.1782952
> print(c4)
[1] -0.2158885
> print(c5)
[1] -0.207948

#for 450
> print(c1)
[1] -0.1902424
> print(c2)
[1] -0.03390291
> print(c3)
[1] -0.1776362
> print(c4)
[1] -0.2251944
> print(c5)
[1] -0.2337897

#for 500
> print(c1)
[1] -0.1872213
> print(c2)
[1] -0.03050068
> print(c3)
[1] -0.17791
> print(c4)
[1] -0.2204073
> print(c5)
[1] -0.2302224

# the correlation barley change with the number of genes added. 

#Lapatinib- Becomes less negatively correlated, around (-0.2249219 - -0.1872213)
#AG1478- Becomes more positivetly regulated, but still bad. 
#Gefitinib- -0.2127953 thru -0.17791- 
#BIBW2992 [1] -0.2754292 theu [1] -0.2204073

#Erlotinib- -0.1905705 thru -0.2302224




Do a t.test/wilxcox test between the ERBB2-amp vs non-ERBB amp. Was not significant. But the Mean on the non-amplifed ERBB2 is higher than amp ERBB2. I would expect the ERBB2 amplified samples to have high prob. than non-ERBB2 because they usually have high EGFR.

```{r}
summary(ICBP_Probs_Drugs$Transcriptional.subtype...ERBB2.status)
plot(ICBP_Probs_Drugs$Transcriptional.subtype...ERBB2.status)
ERRB2amp1=subset(ICBP_Probs_Drugs,ICBP_Probs_Drugs$Transcriptional.subtype...ERBB2.status=="ERBB2-amp")
ERRB2amp1
ERRB2amp2=subset(ICBP_Probs_Drugs,ICBP_Probs_Drugs$Transcriptional.subtype...ERBB2.status=="ERBB2Amp")
class(ERRB2amp2)
ERRB2amp=rbind(ERRB2amp1, ERRB2amp2)
ERRB2amp
summary(ERRB2amp) #alot of high prob and low probs.
dim(ERRB2amp) #21 ERBB2 Amps
hist(ERRB2amp$Probability)

NonERRB1=subset(ICBP_Probs_Drugs,ICBP_Probs_Drugs$Transcriptional.subtype...ERBB2.status!="ERBB2-amp" )
NonERRB1
NonERBB=subset(NonERRB1,NonERRB1$Transcriptional.subtype...ERBB2.status!="ERBB2Amp")
NonERBB
summary(NonERBB)
hist(NonERBB$Probability)

boxplot(ERRB2amp$Probability,NonERBB$Probability) #higer in nonERBB
t.test(ERRB2amp$Probability,NonERBB$Probability) #0.42
wilcox.test(ERRB2amp$Probability,NonERBB$Probability) #0.55
```


It looks like the NonERBB amplifed are more sensitive to the the EGFR inhibiotors than the ERBB AMP
```{r}
cor(ERRB2amp$Probability,ICBP_Probs_Drugs$Lapatinib, use = "pairwise.complete.ob" ) #not working
t.test(ERRB2amp$Probability,NonERBB$Probability)
```

