 ---
title: "multipathway_ASSIGN"
author: "Shelley MacNeil"
date: "Feb 16, 2016"
---
This script will 1) filter CCLE breast cancer cell lines, 2) make single and multi-pathway based predictions using ASSIGN, and 3) Correlate pathway predictions with drug response. 


Import ASSIGN 
```{r,echo=FALSE,cache=TRUE,include=FALSE}
library(sva)
library(ASSIGN)
source("~/Documents/ThesisWork/GitRepos/bild_signatures/Rmarkdowns_scripts/ICBP/23Feb15_multi_icbp.Rmd")
```


Reading in the HMEC signatures
```{r include=FALSE,echo=FALSE}
signatures<-as.matrix(read.table("~/Documents/ThesisWork/GitRepos/bild_signature_validation_old_repo/Datasets/GFP18_AKT_BAD_HER2_IGF1R_RAF_ERK.tpmlog",sep='\t',row.names=1,header=1))
control<-subset(signatures, select=GFP.1:GFP.12)
her2<-subset(signatures, select=HER2.1:HER2.6)
akt<-subset(signatures,select=AKT.1:AKT.6)
bad<-subset(signatures,select=BAD.1:BAD.6)
igf1r<-subset(signatures,select=IGF1R.1:IGF1R.6)
validated_signatures<-cbind(control,akt,bad,her2,igf1r)
dim(validated_signatures)
```

Preparing CCLE data: read in CCLE Meta data and filter out the breast cancer cell lines to merge with expression data later
```{r}
#Metadata
CCLE_Meta_data= as.matrix(read.table("~/Documents/ThesisWork/CCLE_Data/CCLE_RNASeq_Metadata.txt", sep='\t', stringsAsFactors=FALSE, header=1, row.names=1))
head(CCLE_Meta_data)

#determine how many cells lines for each cancer type
CCLE_MetaData_Summary = summary(CCLE_Meta_data, maxsum=31)
CCLE_MetaData_Summary= CCLE_MetaData_Summary[1:22,1]
split_summary=do.call(rbind.data.frame, strsplit(CCLE_MetaData_Summary, ":"))
View(split_summary)
rownames(split_summary)= split_summary[,1]
colnames(split_summary)=c("Cell Line", "Freq")
#split_summary=split_summary[-1]
barplot(as.numeric(split_summary[,2]),names.arg = split_summary[,1],main = "Frequency of type of cell lines in CCLE database",cex.names = 0.5)

#write cell line cancer type frequencies to a file and plot in excel, can't figure out how to plot that dataframe
CCLE_cellline_frequency_file="~/Documents/ThesisWork/GitRepos/bild_signatures/CCLE_cancertype_freqs.txt"
write.table(split_summary,CCLE_cellline_frequency_file,sep='\t', col.names = NA,quote=F)
system("cat ~/Documents/ThesisWork/GitRepos/bild_signatures/CCLE_cancertype_freqs.txt ")

# subset the CCLE breast cancer cell lines
CCLE_Breast=subset(CCLE_Meta_data, grepl("BRCA", CCLE_Meta_data[,1]))
head(CCLE_Breast)
```

Filter out the CCLE Breast Cancer Cell RNA-seq expression data
```{r}
# Read in RNA-seq CCLE data (935 cell lines)
CCLE_expression_data<-read.table("~/Documents/ThesisWork/CCLE_Data/CCLE_RNASeq_TPMlog.txt", sep='\t', check.names = FALSE, stringsAsFactors=FALSE, header=1, row.names=1)
CCLE_expression_data_transposed= t(CCLE_expression_data) #tranpose so we can merge with metadata

#Keep only the breast cell lines and save to a file 1) with meta data 2) with out meta data
CCLE_Expression_Breast=merge(CCLE_Breast, CCLE_expression_data_transposed, by=0) # 56 breast cell lines left 
rownames(CCLE_Expression_Breast)=CCLE_Expression_Breast[,3]
rownames(CCLE_Expression_Breast)

#remove the metadata so it won't mess up the transpose
CCLE_Breast_Metadata_Removed=CCLE_Expression_Breast[,11:ncol(CCLE_Expression_Breast)]
View(head(CCLE_Breast_Metadata_Removed))
rownames(CCLE_Breast_Metadata_Removed)
# Transpose again so the genes are row names, becomes a matrix
CCLE_Breast_Metadata_Removed=t(CCLE_Breast_Metadata_Removed)

#save the Breast only RNA-seq CCLE data
CCLE_Breast_RNASeqFile_no_metadata="~/Documents/ThesisWork/GitRepos/bild_signatures/CCLE_Breast_RNAseq_TPMlog.txt"
CCLE_Breast_RNASeq_no_meta=write.table(CCLE_Breast_Metadata_Removed,CCLE_Breast_RNASeqFile_no_metadata, sep='\t', col.names = NA,quote=F)
system("cat ~/Documents/ThesisWork/GitRepos/bild_signatures/CCLE_Breast_RNAseq_TPMlog.txt | head")
CCLE_Breast_Metadata_Removed=read.table("~/Documents/ThesisWork/GitRepos/bild_signatures/CCLE_data/CCLE_Breast_RNAseq_TPMlog.txt", sep='\t', check.names = FALSE, stringsAsFactors=FALSE, header=1, row.names=1)
View(CCLE_Breast_Metadata_Removed)



```

Filter low varying genes from the signatures and batch adjust CCLE and HMEC signatures 
```{r}
# filtering low variance genes in the HMECS, started with 23367 genes
validated_signatures_filtered <-validated_signatures[apply(validated_signatures[,1:35]==0,1,mean) < 0.85,]
dim(validated_signatures_filtered) #18116

signatures_CCLE_filtered = merge_drop(validated_signatures_filtered,CCLE_Breast_Metadata_Removed,by=0)
dim(signatures_CCLE_filtered) #91
View(head(signatures_CCLE_filtered))
head(signatures_CCLE_filtered[36 ])
#tell pcaplot how many of each thing you have?
sub<-c(12,6,6,5,6,56)
sub
pcaplot(signatures_CCLE_filtered,sub)

# match the batch matrix
batch1_CCLE<-as.matrix(cbind(c(colnames(validated_signatures_filtered),colnames(CCLE_Breast_Metadata_Removed)),c(rep(1,length(colnames(validated_signatures_filtered))),rep(2,length(colnames(CCLE_Breast_Metadata_Removed))))))
                                                                                                                                                                     # Add the HMECSs as a covariate
batches_w_HMECS_as_covar<-as.matrix(cbind(c(colnames(validated_signatures_filtered),colnames(CCLE_Breast_Metadata_Removed)),c(rep(1,length(colnames(validated_signatures_filtered))),rep(2,length(colnames(CCLE_Breast_Metadata_Removed)))),c(rep(1,12),rep(2,23),rep(1,56))))

#GTP as covar
batches_w_GFP_as_covar<-as.matrix(cbind(c(colnames(validated_signatures_filtered),colnames(CCLE_Breast_Metadata_Removed)),c(rep(1,length(colnames(validated_signatures_filtered))),rep(2,length(colnames(CCLE_Breast_Metadata_Removed)))),c(rep(1,12),rep(2,23),rep(2,56))))
batches_w_GFP_as_covar

batches_w_CCLE_as_covar<-as.matrix(cbind(c(colnames(validated_signatures_filtered),colnames(CCLE_Breast_Metadata_Removed)),c(rep(1,length(colnames(validated_signatures_filtered))),rep(2,length(colnames(CCLE_Breast_Metadata_Removed)))),c(rep(1,12),rep(1,23),rep(2,56))))

mod <- model.matrix(~as.factor(batches_w_HMECS_as_covar[,3]))
mod2 <- model.matrix(~as.factor(batches_w_GFP_as_covar[,3]))
mod3 = model.matrix(~as.factor(batches_w_CCLE_as_covar[,3]))
mod3

combat_expr1_CCLE<-ComBat(dat=signatures_CCLE_filtered, batch=batch1_CCLE[,2], mod=NULL, numCovs=NULL)
combat_expr2_with_covars<-ComBat(dat=signatures_CCLE_filtered, batch=batches_w_HMECS_as_covar[,2], mod=mod, numCovs=NULL)
combat_expr3_with_covars_GFP<-ComBat(dat=signatures_CCLE_filtered, batch=batches_w_GFP_as_covar[,2], mod=mod2, numCovs=NULL)
# does not work to put the CCLE as the covar 
#combat_expr4_with_covars_CCLE<-ComBat(dat=signatures_CCLE_filtered, batch=batches_w_CCLE_as_covar[,2], mod=mod3, numCovs=NULL)

pcaplot(combat_expr1_CCLE,sub)
pcaplot(combat_expr2_with_covars,sub) # still have those outliers
pcaplot(combat_expr3_with_covars_GFP,sub) # still has outliers

#subset Combat adjusted values
c_gfp<-subset(combat_expr1, select=GFP.1:GFP.12)
c_akt<-subset(combat_expr1, select=AKT.1:AKT.6)
c_bad<-subset(combat_expr1, select=BAD.1:BAD.6)
c_her2<-subset(combat_expr1, select=HER2.1:HER2.6)
c_igf1r<-subset(combat_expr1, select=IGF1R.1:IGF1R.6)
CCLE_testing_data=combat_expr1_CCLE[,36:ncol(combat_expr1_CCLE)]

```



Run ASSIGN for single pathways
```{r}
#1. HER2
train_her<-cbind(c_gfp,c_her2)
trainingLabelha<-list(control=list(her2=1:12),her2=13:17)
dir.create("~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/CCLE_ASSIGN_Results/Single/Her2")
assign_easy_multi(trainingData = train_her,test=CCLE_testing_data,trainingLabel1 = trainingLabelha, g=15,out_dir_base = "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/CCLE_ASSIGN_Results/Single/Her2")

#2. AKT
train_akt<-cbind(c_gfp,c_akt)
head(train_akt)
trainingLabel_akt<-list(control=list(akt=1:12),akt=13:18)
trainingLabel_akt
dir.create("~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/CCLE_ASSIGN_Results/Single/AKT")
assign_easy_multi(trainingData = train_akt,test=CCLE_testing_data,trainingLabel1 = trainingLabel_akt,g=150,out_dir_base = "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/CCLE_ASSIGN_Results/Single/AKT")

#3. BAD
train_bad<-cbind(c_gfp,c_bad)
trainingLabel_bad<-list(control=list(bad=1:12),bad=13:18)
dir.create( "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/CCLE_ASSIGN_Results/BAD")
assign_easy_multi(trainingData =train_bad,test=CCLE_testing_data,trainingLabel1 = trainingLabel_bad,g=150,out_dir_base = "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/CCLE_ASSIGN_Results/Single/BAD")

#4. IGF1R
train_igfr<-cbind(c_gfp,c_igf1r)
trainingLabel_igfr<-list(control=list(igf1r=1:12),igf1r=13:18)
dir.create( "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/CCLE_ASSIGN_Results/IGF1R")
assign_easy_multi(trainingData =train_igfr,test=CCLE_testing_data,trainingLabel1 = trainingLabel_igfr,g=100,out_dir_base = "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/CCLE_ASSIGN_Results/IGF1R")
```


run ASSIGN for multi-pathway combinations
```{r}
#############trying two pathways at a time in multipathway#############
#1. HER2 & AKT
trainha<-cbind(c_gfp,c_akt,c_her2)
testha<-combat_expr1[,36:ncol(combat_expr1)]
trainingLabelha<-list(control=list(akt=1:12,her2=1:12),akt=13:18,her2=19:23)
dir.create("~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/CCLE_ASSIGN_Results/Her2_AKT")
assign_easy_multi(trainingData = trainha,test=testha,trainingLabel1 = trainingLabelha,g=c(150,15),out_dir_base = "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/CCLE_ASSIGN_Results/Multipathway/Her2_AKT")

#2. HER2 & BAD
trainhb<-cbind(c_gfp,c_bad,c_her2)
trainingLabelhb<-list(control=list(bad=1:12,her2=1:12),bad=13:18,her2=19:23)
dir.create( "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/CCLE_ASSIGN_Results/Her2_BAD")
assign_easy_multi(trainingData = trainhb,test=CCLE_testing_data,trainingLabel1 = trainingLabelhb,g=c(150,15),out_dir_base = "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/CCLE_ASSIGN_Results/Multipathway/Her2_BAD")

#3. HER2 & IGF1R
trainhi<-cbind(c_gfp,c_igf1r,c_her2)
trainingLabelhi<-list(control=list(igf1r=1:12,her2=1:12),igf1r=13:18,her2=19:23)
dir.create( "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/Her2_IGF1R")
assign_easy_multi(trainingData =trainhi,test=CCLE_testing_data,trainingLabel1 = trainingLabelhi,g=c(100,15),out_dir_base = "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/Multipathway/Her2_IGF1R")

#4. AKT & BAD
trainab<-cbind(c_gfp,c_akt,c_bad)
trainingLabelab<-list(control=list(akt=1:12,bad=1:12),akt=13:18,bad=19:24)
dir.create( "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/AKT_BAD")
assign_easy_multi(trainingData = trainab,test=CCLE_testing_data,trainingLabel1 = trainingLabelab,g=c(150,150),out_dir_base = "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/Multipathway/AKT_BAD")

#5. AKT & IGF1R
trainai<-cbind(c_gfp,c_akt,c_igf1r)
trainingLabelai<-list(control=list(akt=1:12,igf1r=1:12),akt=13:18,igf1r=19:24)
dir.create( "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/AKT_IGF1R")
assign_easy_multi(trainingData = trainai,test=CCLE_testing_data,trainingLabel1 = trainingLabelai,g=c(150,100),out_dir_base = "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/Multipathway/AKT_IGF1R")

#6. BAD & IGF1R
trainbi<-cbind(c_gfp,c_bad,c_igf1r)
trainingLabelbi<-list(control=list(bad=1:12,igf1r=1:12),bad=13:18,igf1r=19:24)
dir.create( "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/BAD_IGF1R")
assign_easy_multi(trainingData = trainbi,test=CCLE_testing_data,trainingLabel1 = trainingLabelbi,g=c(150,100),out_dir_base = "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/Multipathway/BAD_IGF1R")

#############trying three pathways at a time in multipathway#############
#1. HER2, AKT & BAD
trainhab<-cbind(c_gfp,c_akt,c_bad,c_her2)
testhab<-combat_expr1[,36:90]
trainingLabelhab<-list(control=list(akt=1:12,bad=1:12,her2=1:12),akt=13:18,bad=19:24,her2=25:29)
dir.create( "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/AKT_BAD_HER2")
assign_easy_multi(trainingData = trainhab,test=CCLE_testing_data,trainingLabel1 = trainingLabelhab,g=c(150,150,15),out_dir_base = "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/Multipathway/AKT_BAD_HER2")

#2. HER2, BAD & IGF1R
trainhbi<-cbind(c_gfp,c_igf1r,c_bad,c_her2)
testhbi<-combat_expr1[,36:90]
trainingLabelhbi<-list(control=list(igf1r=1:12,bad=1:12,her2=1:12),igf1r=13:18,bad=19:24,her2=25:29)
dir.create( "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/IGF1R_BAD_HER2")
assign_easy_multi(trainingData = trainhbi,test=CCLE_testing_data,trainingLabel1 = trainingLabelhbi,g=c(100,150,15),out_dir_base = "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/Multipathway/IGF1R_BAD_HER2")

#3. AKT, BAD & IGF1R
trainabi<-cbind(c_gfp,c_akt,c_bad,c_igf1r)
dim(trainabi)
head(trainabi)
trainingLabelabi<-list(control=list(akt=1:12,bad=1:12,igf1r=1:12),akt=13:18,bad=19:24,igf1r=25:30)
dir.create( "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/CCLE_ASSIGN_Results/AKT_BAD_IGF1R") 
assign_easy_multi(trainingData = trainabi,test=CCLE_testing_data, trainingLabel1 = trainingLabelabi,g=c(150,150,100), out_dir_base = "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/CCLE_ASSIGN_Results/Multipathway/AKT_BAD_IGF1R")

########################trying all four at once#####################
trainhall<-cbind(c_gfp,c_akt,c_bad,c_her2,c_igf1r)
testall<-combat_expr1[,36:90]
trainingLabel<-list(control=list(akt=1:12,bad=1:12,her2=1:12,igf1r=1:12),akt=13:18, bad=19:24,her2=25:29,igf1r=30:35)
dir.create( "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/all_4")
assign_easy_multi(trainingData = trainhall,test=CCLE_testing_data,trainingLabel1 = trainingLabel,g=c(150,150,15,100),out_dir_base = "~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/Multipathway/all_4")

```

Read back in all the predictions into one matrix for correlations
```{r include=FALSE}
setwd("~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/CCLE_ASSIGN_Results/Multipathway/")
filenames_adaptive<-system("ls */adap*/pathway_activity_testset*", intern=TRUE)
filenames_nonadaptive<-system("ls */non*/pathway_activity_testset*", intern=TRUE)
filenames_adaptive
filenames_nonadaptive
length(filenames_adaptive)

for(i in 1:length(filenames_adaptive))
  {
   f<-read.csv(filenames_adaptive[i], header=1,row.names=1) ###reading in the filess one at a time
   print(f)
   colnames(f)<-paste(filenames_adaptive[i],colnames(f),sep='/')
  if(i==1){
    data_adaptive<-f
    }
  else{
    data_adaptive<-cbind(data_adaptive,f)
    }
  }

View(data_adaptive)
write.table(data_adaptive,"~/Desktop/CCLE_multipathway_predictions_adaptive.txt",sep='\t', col.names = NA,quote=F)

for(i in 1:length(filenames_nonadaptive))
  {
   f<-read.csv(filenames_nonadaptive[i], header=1,row.names=1) ###reading in the filess one at a time
  colnames(f)<-paste(filenames_nonadaptive[i],colnames(f),sep='/')
  if(i==1){
    data_nonadaptive<-f
    }
  else{
    data_nonadaptive<-cbind(data_nonadaptive,f)
    }
  }

View(data_nonadaptive)
write.table(data_nonadaptive,"~/Desktop/CCLE_multipathway_predictions_nonadpative.txt",sep='\t', col.names = NA,quote=F)
```

File single pathway files
```{r include=FALSE}
setwd("~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/CCLE_ASSIGN_Results/Single")
filenames_adaptive_single<-system("ls */adap*/pathway_activity_testset*", intern=TRUE)
filenames_nonadaptive_single<-system("ls */non*/pathway_activity_testset*", intern=TRUE)
filenames_adaptive_single


for(i in 1:length(filenames_adaptive_single))
  {
   f<-read.csv(filenames_adaptive_single[i], header=1,row.names=1) ###reading in the filess one at a time
   print(f)
   colnames(f)<-paste(filenames_adaptive_single[i],colnames(f),sep='/')
  if(i==1){
    data_adaptive_single<-f
    }
  else{
    data_adaptive_single<-cbind(data_adaptive_single,f)
    }
  }

View(data_adaptive_single)

write.table(data_adaptive_single,"~/Desktop/CCLE_sinlgepathway_predictions_adaptive.txt",sep='\t', col.names = NA,quote=F)

for(i in 1:length(filenames_nonadaptive_single))
  {
   f<-read.csv(filenames_nonadaptive_single[i], header=1,row.names=1) ###reading in the filess one at a time
  colnames(f)<-paste(filenames_nonadaptive_single[i],colnames(f),sep='/')
  if(i==1){
    data_nonadaptive_single<-f
    }
  else{
    data_nonadaptive_single<-cbind(data_nonadaptive_single,f)
    }
  }

View(data_nonadaptive_single)
write.table(data_nonadaptive_single,"~/Desktop/CCLE_singlepathway_predictions_nonadapative.txt",sep='\t', col.names = NA,quote=F)
```


Read in files single and multi apaptive_apaptive
```{r}
setwd("~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/CCLE_ASSIGN_Results/Single")
filenames_single_adaptive_adaptive<-system("ls */adap_adap*/pathway_activity_testset*", intern=TRUE)
filenames_single_adaptive_adaptive

for(i in 1:length(filenames_single_adaptive_adaptive))
  {
   f<-read.csv(filenames_single_adaptive_adaptive[i], header=1,row.names=1) ###reading in the filess one at a time
   print(f)
   colnames(f)<-paste(filenames_single_adaptive_adaptive[i],colnames(f),sep='/')
  if(i==1){
    data_adaptive_adap_single<-f
    }
  else{
    data_adaptive_adap_single<-cbind(data_adaptive_adap_single,f)
    }
  }

View(data_adaptive_adap_single)

write.table(data_adaptive_single,"~/Desktop/CCLE_single_predictions_adaptiveB_adaptiveS.txt",sep='\t', col.names = NA,quote=F)

setwd("~/Documents/ThesisWork/GitRepos/bild_signatures/ASSIGN_Results_Ignore_too_big/CCLE_ASSIGN_Results/Multipathway")
filenames_multi_adaptive_adaptive<-system("ls */adap_adap*/pathway_activity_testset*", intern=TRUE)
filenames_multi_adaptive_adaptive

for(i in 1:length(filenames_multi_adaptive_adaptive))
  {
   f<-read.csv(filenames_multi_adaptive_adaptive[i], header=1,row.names=1) ###reading in the filess one at a time
  colnames(f)<-paste(filenames_multi_adaptive_adaptive[i],colnames(f),sep='/')
  if(i==1){
    data_multi_adaptive_adaptive<-f
    }
  else{
    data_multi_adaptive_adaptivee<-cbind(data_multi_adaptive_adaptive,f)
    }
  }

View(data_multi_adaptive_adaptive)
write.table(data_multi_adaptive_adaptive,"~/Desktop/CCLE_multi_predictions_adapativeB_adaptiveS.txt",sep='\t', col.names = NA,quote=F)

```

Correlate Adaptive results with Non-apative results
```{r}
Cors_adap_nonadap= cor(data_nonadaptive,data_adaptive, method= "spearman")
write.table(Cors_adap_nonadap,"~/Desktop/Corelations_adap_nonadap_CCLE_predictions.txt",sep='\t', col.names = NA,quote=F)
View(Cors_adap_nonadap)
```


Read back in the files
```{r}

CCLE_multi_adap<-read.delim("~/Desktop/CCLE_multipathway_predictions_adaptive.txt", header=1, sep='\t',row.names=1)
CCLE_multi_adap_cors=cor(CCLE_multi_adap, CCLE_multi_adap, use="na.or.complete", method="spearman")
View(CCLE_multi_adap_cors[22:25,22:25])

CCLE_multi_nonadap<-read.delim("~/Desktop/CCLE_multipathway_predictions_nonadpative.txt", header=1, sep='\t',row.names=1)
CCLE_multi_nonadap_cors=cor(CCLE_multi_nonadap, CCLE_multi_nonadap, use="na.or.complete", method="spearman")
View(CCLE_multi_nonadap_cors[22:25,22:25])

CCLE_single_nonadap<-read.delim("~/Desktop/CCLE_singlepathway_predictions_nonadapative.txt", header=1, sep='\t',row.names=1)
CCLE_single_nonadap_cors=cor(CCLE_single_nonadap, CCLE_single_nonadap, use="na.or.complete", method="spearman")
View(CCLE_single_nonadap_cors)

CCLE_single_adap<-read.delim("~/Desktop/CCLE_sinlgepathway_predictions_adaptive.txt", header=1, sep='\t',row.names=1)
CCLE_single_adap_cors=cor(CCLE_single_adap, CCLE_single_adap, use="na.or.complete", method="spearman")
View(CCLE_single_adap_cors)
```

Correlate with the IC50s
```{r}
CCLE_drug_data=
  
```






```{r echo=FALSE}
time<-format(Sys.time(),"%a %b %d %X %Y")
```
This analysis was run on `r time` 

